---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@media (prefers-color-scheme: light) {
  body {
    color: black;
    background-color: white;
  }
}
@media (prefers-color-scheme: dark) {
  body {
    color: white;
    background-color: black;
  }
}
body {
  display: flex;
  flex-wrap: wrap;
}
h1 {
  text-align: center;
}
h2 {
  text-align: center;
}
```

## Project 2 (Advertisement colours) for STATS 220

# **BAR CHARTS**

```{r fig.width = 12, fig.height = 12}
# fig.width = 12, fig.height = 12
### COMMENTED SECTION ###
# import librarie(s)
library(tidyverse)
# reading csv file
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQt3NGFc7ZR_dFFon_w3PZS3OL_t3mg4Sf8rJ_IAKFnpIh2PcomBgyRgDxjm55T1pIhAHjZZL1pnzYo/pub?output=csv") 
# renaming variables
latest_data = rename(logged_data, 
                     primary_colours = 2,
                     primary_effective = 3,
                     secondary_colours = 4,
                     secondary_effective = 5,
                     colour_schemes = 6,
                     colour_schemes_effective = 7,
                     overall_rating = 8)
# making the red, yellow into red and yellow (i.e. making them separated)
latest_data_sep <- latest_data %>%
  separate_rows(c(primary_colours, secondary_colours, colour_schemes), sep=", ")
# one summary value
#paste("Blue is used for a number of", sum(latest_data_sep$primary_colours == "Blue"), "times.",
#      "Red is used for a number of", sum(latest_data_sep$primary_colours == "Red"), "times.",
#      "Yellow is used for a number of", sum(latest_data_sep$primary_colours == "Yellow"), "times.")
# another summary value
#paste("The mean overall score is ", mean(latest_data$overall_rating), ".", sep="")
# extras
#paste("The median overall score is ", median(latest_data$overall_rating), ".", sep="")

```

## Primary Colours
```{r fig.width = 12, fig.height = 12}
# bar charts
# making the simple correlation graphs
#primary_colours_graph
latest_data_sep %>% ggplot() + geom_bar(aes(primary_colours, fill = primary_effective))+ 
  labs(title = "Primary colours amount vs effectiveness", x="Primary colours", y="Count", fill="Is the primary colour\neffective in drawing attention?")

```

## Secondary Colours
```{r fig.width = 12, fig.height = 12}
#secondary_colours_graph
latest_data_sep %>% ggplot() + geom_bar(aes(secondary_colours, fill = secondary_effective))+ 
  labs(title = "Secondary colours amount vs effectiveness", x="Secondary colours", y="Count", fill="Is the secondary colour\neffective in drawing attention?")
```

## Colour Schemes
```{r fig.width = 12, fig.height = 12}
#colour_schemes_graph
latest_data_sep %>% ggplot() + geom_bar(aes(colour_schemes, fill = colour_schemes_effective))+ 
  labs(title = "Colour schemes amount vs effectiveness", x="Colour schemes", y="Count", fill="Is the colour scheme\neffective in drawing attention?")
```

# **SUMMARY VALUES**
Blue is used for a number of `r sum(latest_data_sep$primary_colours == "Blue")` times.  
Red is used for a number of `r sum(latest_data_sep$primary_colours == "Red")` times.  
Yellow is used for a number of `r sum(latest_data_sep$primary_colours == "Yellow")` times.  
The mean overall score is `r mean(latest_data$overall_rating)`.   
The median overall score is `r median(latest_data$overall_rating)`.   
